---
title: "Naming conventions"
author: "Hallie Eilerts-Spinelli"
date: "2023-03-08"
output:
  md_document:
    variant: markdown_github
editor_options: 
  chunk_output_type: console
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#devtools::install_github(repo="haozhu233/kableExtra", ref="a6af5c0")
library(kableExtra)
library(tidyr)

```


## Naming conventions

This file details the naming conventions used in the master workflow document which details all modelling processes from start to finish. 

Naming conventions result in improvements in terms of communication, code integration, consistency and clarity. While many of the names below were gleaned from the existing code, they do not match the code exactly. If/when we try to standardize naming conventions across all code, the notation system described here could be a starting point.

All entities should be named following the format: **class_objectINSTANCE_source**

```{r, echo=FALSE, results='asis'}
df_class <- data.frame(eg = c("dth","p","db","mf","fm","res"),
                       egdesc = c("death counts", "proportions", "database", "model frame", "fitted model", "results"))
df_class$component <- "class"
df_class$desc <- "Type of information contained in the object."
df_class <- df_class[order(df_class$eg),]

df_obj <- data.frame(eg = c("pred","env","<cause of death>","<age/sex group>"),
                       egdesc = c("prediction", "envelope", "e.g., meas, tb, collectvio", "0to1, 1to59, 5to9, 10to14, 15to19f, 15to19m"))
df_obj <- df_obj[order(df_obj$eg),]
df_obj$component <- "object"
df_obj$desc <- "Name of object."

df_inst <- data.frame(eg = c("cf/ci","end/epi", "hmm/lmm", "resp/nonr", "<country>"),
                       egdesc = c("crisis-free/crisis-included", "endemic/epidemic", "high/low mortality modelled", "respiratory/non-respiratory", "e.g., China, India"))
df_inst <- df_inst[order(df_inst$eg),]
df_inst$component <- "instance"
df_inst$desc <- "Distinguishes different instances of the same object."


df_source <- data.frame(eg = c("igme","who", "wpp"),
                       egdesc = c("UN Inter-agency Group of Mortality Estimation", "World Population Prospects", "World Health Organization"))
df_source <- df_source[order(df_source$eg),]
df_source$component <- "source"
df_source$desc <- "Indicates the source of the entity, if external. Written in all uppercase. Paired instances should have the same number of letters."

df_tab <- rbind(df_class, df_obj, df_inst, df_source)
df_tab <- df_tab[,c("component","desc","eg","egdesc")]
names(df_tab) <- c("Component",	"Description",	"Example Values",	"Value Description")

kable(df_tab, "html", row.names = FALSE) %>%
  kable_paper(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "middle")
```

